---
title: "2_data_processing"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Loading, setting up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r load-packages} 
library(here)
library(tidyverse)
library(quanteda)
library(topicmodels)
library(ldatuning)
```

```{r, load-data}
data_path <- here("data", "processed")
file_names <- list.files(data_path)
file_paths <- file.path(data_path, file_names)
d <- file_paths %>% set_names() %>% map_df(read_csv)
write_csv(d, here("data", "combined-data.csv"))
```

```{r, clean-text-preliminary}
d$post <- tokens(d$post, remove_url = TRUE, remove_numbers = TRUE)
```

# N-grams analysis

## Words (grams)

```{r, grams}
my_dfm <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE)
my_dfm
topfeatures(my_dfm, 20)
```

## Pairs of words (bi-grams) - with and without stemming after creating the bi-gram

```{r, bi-grams}
my_dfm_bi <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE, ngrams = 2)
my_dfm_bi
topfeatures(my_dfm_bi, 20)

my_dfm_bi_s <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE, ngrams = 2) %>% 
  dfm_remove(pattern = c(paste0("^", stopwords("english"), "_"), 
                         paste0("_", stopwords("english"), "$")), 
             valuetype = "regex")
my_dfm_bi_s
topfeatures(my_dfm_bi_s, 20)
```

## Groups of three words (tri-grams)- with and without stemming after creating the tri-gram

```{r, tri-grams}
my_dfm_tri <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE, ngrams = 3)
my_dfm_tri
topfeatures(my_dfm_tri, 20)

my_dfm_tri_s <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE, ngrams = 3) %>% 
  dfm_remove(pattern = c(paste0("^", stopwords("english"), "_"), 
                         paste0("_", stopwords("english"), "$")), 
             valuetype = "regex")
my_dfm_tri_s
topfeatures(my_dfm_tri_s, 20)
```

## Groups of four words (quad-grams) - with and without stemming after creating the quad-gram

```{r, quad-grams}
my_dfm_quad <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE, ngrams = 4)
my_dfm_quad
topfeatures(my_dfm_quad, 20)

my_dfm_quad_s <- dfm(d$post, remove = stopwords("english"), stem = TRUE, remove_punct = TRUE, ngrams = 4) %>% 
  dfm_remove(pattern = c(paste0("^", stopwords("english"), "_"), 
                         paste0("_", stopwords("english"), "$")), 
             valuetype = "regex")
my_dfm_quad_s
topfeatures(my_dfm_quad_s, 20)
```

# Topic models

## With words (grams)

```{r, finding-topics-numbers-grams}
my_dtm <- my_dfm[ntoken(my_dfm) > 0,]
my_dtm <- convert(my_dtm, to = "topicmodels")

result <- FindTopicsNumber(
  my_dtm,
  topics = c(2, 5, 10, 15, 20, 25, 30, 35),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  mc.cores = 4L,
  verbose = TRUE
)
FindTopicsNumber_plot(result)
```
## With pairs of words (bi-grams, stemmed)

```{r, finding-topics-numbers-bi-grams-stemmed}
my_dtm_1 <- my_dfm[ntoken(my_dfm_bi_s) > 0,]
my_dtm_1 <- convert(my_dtm_1, to = "topicmodels")

result1 <- FindTopicsNumber(
  my_dtm_1,
  topics = c(2, 5, 10, 15, 20, 25, 30, 35),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  mc.cores = 4L,
  verbose = TRUE
)
FindTopicsNumber_plot(result)
```